---
title: "Activity: Nuclear Reactors"
author: "Tsu-yen Su"
output: html_noteboo
---

```{r}
library(tidyverse)

```

## Scrape the Data 

```{r}
library(rvest)

page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css= "table") %>%
  html_table(fill = TRUE)


```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

The table is tidy because each cell has its own value.


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
tableList[[21]][ ,1:9]
Japan <-
  tableList[[21]][ ,1:9] %>%
  filter(row_number() > 1) %>%
  rename(name = Plantname, 
         reactor = UnitNo.,
         model = Type,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = Beginbuilding,
         operation = Commercialoperation, 
         closure = Closed) %>%
mutate(construction = dmy(construction),
         operation = dmy(operation),
         closure = dmy(closure),
         netMW = as.numeric(netMW),
         country = "Japan")

```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
tableList[[10]][ ,1:9]
China <-
  tableList[[10]][ ,1:9] %>%
  filter(row_number() > 1) %>%
  rename(name = Plantname, 
         reactor = UnitNo.,
         model = Type,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = Beginbuilding,
         operation = Commercialoperation, 
         closure = Closed) %>%
  mutate(construction = dmy(construction),
         operation = dmy(operation),
         closure = dmy(closure),
         netMW = as.numeric(netMW),
         country = "China")

combined_data <- bind_rows(Japan, China)

ggplot(combined_data, aes(x = construction, xend= operation, y=name,yend=name, color = model)) +
  geom_segment() +
  geom_point(aes(y=name,x=closure,shape= status)) +
  labs(title = "Net Generation Capacity vs. Date of Construction",
       x = "Dat",
       y = "Net Generation Capacity (MW)",
       color = "Reactor Type")
library(ggplot2)
```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}


```